\LARGE \bf The Battle for Filter Supremacy: A Comparative Study of the Multi-State Constraint Kalman Filter and the Sliding Window Filter

### 2014-12-31 Report/project_report.tex
Made figures with subfigures span both columns

\begin{figure}
    \centering
    \subfigure {
        \includegraphics[width=0.48\textwidth]{figs/NST_trans}
        \label{fig:nullspace:trans_err}
    }

    \subfigure {
        \includegraphics[width=0.48\textwidth]{figs/NST_rot}
        \label{fig:nullspace:rot_err}
    }

    \caption{Effect of correlation between measurement noise and filter state on MSCKF performance. The correlation between the measurement noise and the state causes the filter estimates to drift further from the true values than with a modified, de-correlated measurement noise.}
    \label{fig:nullspace}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.48\textwidth]{figs/trajectory_groundtruth}
    \caption{Vicon ground truth for sensor head motion and feature positions in the ``Starry Night'' dataset.}
    \label{fig:trajectory_groundtruth}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.48\textwidth]{figs/nVisible_500_1000}
    \caption{Number of visible features in the interval $k\in[500,1000]$. Red points indicate that fewer than three features were visible, while green points indicate at least three features were visible.}
    \label{fig:nVisible_int1}
\end{figure}

@@

\begin{figure}
    \centering
    \subfigure {
        \includegraphics[width=0.48\textwidth]{figs/6-Way-Comparison-500-1000-Trans}
        \label{fig:comp_1:trans_err}
    }

    \subfigure {
        \includegraphics[width=0.48\textwidth]{figs/6-Way-Comparison-500-1000-Rot}
        \label{fig:comp_1:rot_err}
    }

    \caption{Comparison of MSCKF, SWF, and IMU integration for multiple parameter settings on the dataset interval $k\in[500,1000]$. The numbers next to ``MSCKF'' in the legend refer to the minimum and maximum feature track lengths before an EKF update is triggered, while the number next to ``SWF'' refers to the number of states in the sliding window.}
    \label{fig:comp_1}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.48\textwidth]{figs/nVisible_1215_1715}
    \caption{Number of visible features in the interval $k\in[1215,1715]$. Red points indicate that fewer than three features were visible, while green points indicate at least three features were visible.}
    \label{fig:nVisible_int2}
\end{figure}

\begin{figure}
    \centering
    \subfigure {
        \includegraphics[width=0.48\textwidth]{figs/6-Way-Comparison-1215-1715-Trans}
        \label{fig:comp_2:trans_err}
    }

    \subfigure {
        \includegraphics[width=0.48\textwidth]{figs/6-Way-Comparison-1215-1715-Rot}
        \label{fig:comp_2:rot_err}
    }

    \caption{Comparison of MSCKF, SWF, and IMU integration for multiple parameter settings on the dataset interval $k\in[1215,1715]$. The numbers next to ``MSCKF'' in the legend refer to the minimum and maximum feature track lengths before an EKF update is triggered, while the number next to ``SWF'' refers to the number of states in the sliding window.}
    \label{fig:comp_2}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.48\textwidth]{figs/trajectory_groundtruth_100lessnoisy}
    \caption{Modified ``Starry Night'' dataset with 100 synthetic features. The sensor trajectory is identical to the original dataset.}
    \label{fig:trajectory_groundtruth_100lessnoisy}
\end{figure}

@@

\begin{figure}
    \centering
    \subfigure {
        \includegraphics[width=0.48\textwidth]{figs/RMSE-Comparison-Feat-Density-1215-1715-Trans}
        \label{fig:comp_3:trans_err}
    }

    \subfigure {
        \includegraphics[width=0.48\textwidth]{figs/RMSE-Comparison-Feat-Density-1215-1715-Rot}
        \label{fig:comp_3:rot_err}
    }

    \caption{Comparison of Root Mean Squared Error (RMSE) of the MSCKF, SWF, and pure IMU integration for three different synthetic maps generated based on the IMU data in the dataset interval $k\in[1215,1715]$. The numbers next to ``MSCKF'' and ``SWF'' refer to the number of features in the dataset (40, 60 or 100).}
    \label{fig:comp_3}
\end{figure}

>>>>

\begin{figure*}
    \centering
    \subfigure {
        \includegraphics[width=0.45\textwidth]{figs/NST_trans}
        \label{fig:nullspace:trans_err}
    }
    ~
    \subfigure {
        \includegraphics[width=0.45\textwidth]{figs/NST_rot}
        \label{fig:nullspace:rot_err}
    }

    \caption{Effect of correlation between measurement noise and filter state on MSCKF performance. The correlation between the measurement noise and the state causes the filter estimates to drift further from the true values than with a modified, de-correlated measurement noise.}
    \label{fig:nullspace}
\end{figure*}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.45\textwidth]{figs/trajectory_groundtruth}
    \caption{Vicon ground truth for sensor head motion and feature positions in the ``Starry Night'' dataset.}
    \label{fig:trajectory_groundtruth}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.45\textwidth]{figs/nVisible_500_1000}
    \caption{Number of visible features in the interval $k\in[500,1000]$. Red points indicate that fewer than three features were visible, while green points indicate at least three features were visible.}
    \label{fig:nVisible_int1}
\end{figure}

@@

\begin{figure*}
    \centering
    \subfigure {
        \includegraphics[width=0.45\textwidth]{figs/6-Way-Comparison-500-1000-Trans}
        \label{fig:comp_1:trans_err}
    }
    ~
    \subfigure {
        \includegraphics[width=0.45\textwidth]{figs/6-Way-Comparison-500-1000-Rot}
        \label{fig:comp_1:rot_err}
    }

    \caption{Comparison of MSCKF, SWF, and IMU integration for multiple parameter settings on the dataset interval $k\in[500,1000]$. The numbers next to ``MSCKF'' in the legend refer to the minimum and maximum feature track lengths before an EKF update is triggered, while the number next to ``SWF'' refers to the number of states in the sliding window.}
    \label{fig:comp_1}
\end{figure*}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.45\textwidth]{figs/nVisible_1215_1715}
    \caption{Number of visible features in the interval $k\in[1215,1715]$. Red points indicate that fewer than three features were visible, while green points indicate at least three features were visible.}
    \label{fig:nVisible_int2}
\end{figure}

\begin{figure*}
    \centering
    \subfigure {
        \includegraphics[width=0.45\textwidth]{figs/6-Way-Comparison-1215-1715-Trans}
        \label{fig:comp_2:trans_err}
    }
    ~
    \subfigure {
        \includegraphics[width=0.45\textwidth]{figs/6-Way-Comparison-1215-1715-Rot}
        \label{fig:comp_2:rot_err}
    }

    \caption{Comparison of MSCKF, SWF, and IMU integration for multiple parameter settings on the dataset interval $k\in[1215,1715]$. The numbers next to ``MSCKF'' in the legend refer to the minimum and maximum feature track lengths before an EKF update is triggered, while the number next to ``SWF'' refers to the number of states in the sliding window.}
    \label{fig:comp_2}
\end{figure*}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.45\textwidth]{figs/trajectory_groundtruth_100lessnoisy}
    \caption{Modified ``Starry Night'' dataset with 100 synthetic features. The sensor trajectory is identical to the original dataset.}
    \label{fig:trajectory_groundtruth_100lessnoisy}
\end{figure}

@@

\begin{figure*}
    \centering
    \subfigure {
        \includegraphics[width=0.45\textwidth]{figs/RMSE-Comparison-Feat-Density-1215-1715-Trans}
        \label{fig:comp_3:trans_err}
    }
    ~
    \subfigure {
        \includegraphics[width=0.45\textwidth]{figs/RMSE-Comparison-Feat-Density-1215-1715-Rot}
        \label{fig:comp_3:rot_err}
    }

    \caption{Comparison of Root Mean Squared Error (RMSE) of the MSCKF, SWF, and pure IMU integration for three different synthetic maps generated based on the IMU data in the dataset interval $k\in[1215,1715]$. The numbers next to ``MSCKF'' and ``SWF'' refer to the number of features in the dataset (40, 60 or 100).}
    \label{fig:comp_3}
\end{figure*}
